### 2016-03-23 thesis/conclusions.tex
m

In this thesis, we explored scaling relations between the supermassive black hole mass 
and various properties of the host spheroid, 
aiming at a more profound understanding of the co-evolution between SMBHs and their host galaxies. 
A summary of our principal findings and some additional considerations are presented here. 
This Chapter incorporates also some promising future research directions. \\

@@

In Chapter \ref{ch:mn} \citep{paperIII}, 
we analysed the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
and found that in the former early- and late-type galaxies split into two separate correlations, 
whereas in the latter all galaxies -- irrespective of their morphological type -- define a single correlation. 
Our $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
show consistent amount of intrinsic scatter, 
in agreement with the results from \citet{grahamdriver2007}. 
The present dataset allows one to explore also the correlation of black hole mass with 
spheroid central surface density, $\mu_{\rm 0, sph}$, 
and spheroid deprojected central stellar density, $\rho_{\rm *,0,sph}$. \\

@@

have evolved into today's bulges of lenticular and early-type spiral galaxies, 

@@

These galaxies have classical bulges, 
they host some of the most massive black holes known ($10^9 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 10^{10}$), 
but are not the product of major mergers as the majority of today's massive elliptical galaxies. 

>>>>

In this thesis, we explored scaling relations between the supermassive black hole mass 
and various properties of the host spheroid, 
in the pursuit of a more profound understanding of the co-evolution between SMBHs and their host galaxies. 
A summary of our principal findings and some additional considerations are presented here. 
This Chapter incorporates also some promising future research directions. \\

@@

In Chapter \ref{ch:mn} \citep{paperIII}, 
we analysed the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
and found that in the former early- and late-type galaxies split into two separate correlations, 
whereas in the latter relation all galaxies -- irrespective of their morphological type -- define a single correlation. 
Our $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
show consistent amount of intrinsic scatter, 
in agreement with the results from \citet{grahamdriver2007}. 
The present dataset allows one to explore also the correlation of black hole mass with 
spheroid central surface density, $\mu_{\rm 0, sph}$, 
and spheroid deprojected central stellar density, $\rho_{\rm *,0,sph}$. \\

@@

have evolved into today's bulges of lenticular and early-type spiral galaxies (see also \citealt{graham2013review}), 

@@

These galaxies have classical bulges and  
host some of the most massive black holes known ($10^9 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 10^{10}$), 
but they are not the product of major mergers like the majority of today's massive elliptical galaxies. 
